---
title: "242_group_project"
author: "Annie Combs"
date: "November 23, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background Info to Build Code From

### Picking a case study and finding number of tourists there- no need to figure out env quality according to Plantinga. Just focus on tourists and assign a certain number of damage to each and go for a steady state like the fishery stock problem.

### Case Studies We Can Use
### 1.National Parks Data (have $ spent and guest count) EASIEST BY FAR
### 2.I have lots of data on spending in Galapagos
### 3.Costa Rica also an option

## The Fishery Example from HW
## Example 3: Stock Pollutant {.tabset}

This problem involves a stock pollutant that evolves according to $Z_{t+1}=z_t(1-\gamma)+\alpha*q_t$, where $\gamma$ captures how much pollution degrades each period and $\alpha$ captures how much pollution is produced by production $q_t$.  Suppose that production is worth $p$ per unit of output, so net revenues are $pq$.  Damages caused by pollution are $C=aZ_t - bZ_t^2$.  The objective is to maximize the present value of net benefits (PNVB) from time 0 to time 10: 

$$
\max_q \sum^{t=10}_{t=0}\rho^t(pq_t-(aZ_t-bZ_t^2))
$$
subject to $Z_{t+1}=z_t(1-\gamma)+\alpha*q_t$ and $Z_0$ given. Use the following parameter values: $\rho=\frac{1}{1.05}$, p=100, a= 2, b=-0.25,$\gamma=0.2$, $\alpha=2$, and $Z_o$=20. 


### A. 

What is the amount of production $q_t$ in each period according to the solution? 

<span style="color: blue;">**Solution**
</span>



```{r}


# Notice that period is not included as a parameter of the function

obj_fcn_stock<-function(choice,int_state,a,b,gamma,p,alpha,discount){

  
# The state and benefits vectors will have the same length as the choice vector    
  
    #make storage vectors
  state<-vector(mode="numeric",length=length(choice))
  benefits<-vector(mode="numeric",length=length(choice))
  

  #initial state and benefits
  
  
  state[1]=int_state
  
  benefits[1]=p*choice[1]-(a*state[1]-b*state[1]^2)

#  The loop goes from 2 to whatver the length of choice ends up being
    
  for(i in 2:length(choice)){
    
# Add the stock dyanmics
    
    state[i]=state[i-1]*(1-gamma)+alpha*choice[i-1] #Add the time from the choice to the state
    
    
  benefits[i]=p*choice[i]-(a*state[i]-b*state[i]^2)
       
             
  }
  
  
  #define period
  
# Populating a vector with 0,1,... that ends with the length of the benefits vector
  
  t=seq(from=0,length.out=length(benefits))
  
  pv=discount^t*benefits
    
  npv=sum(pv)
  
  return(-npv)
  
  
}


local_opts<-list("algorithm"="NLOPT_LN_COBYLA",xtol_rel=1e-15)
options=list("algorithm"="NLOPT_LN_AUGLAG",xtol_rel=1e-15,maxeval=16000,"local_opts"=local_opts)

# Because I didn't include period as a parameter in the function, I need to define it here.

period=11

#Use lb to say we cannot have negative extraction, ub says extraction cannot exceed 10

out_3a=nloptr(x0=rep(1,period),eval_f=obj_fcn_stock,
              lb=rep(0,period),
              #ub=rep(10,period),
              opts = options,int_state=20,discount=1/1.05,a=2,b=-.25,gamma=0.2,alpha=2,p=100)


ta_solution=round(out_3a$solution,5)

ta_value=round(-out_3a$objective,3)

```



<span style="color: blue;">With a higher price, it is worth it to increase production and have a large stock of Z.
</span>



```{r}
## Function for making a table

stock<-function(choice,int_state=20,a=2,b=-0.25,gamma=.2,p=100,alpha=2,discount=1/1.05){
  
  
    #make storage vectors
  state<-vector(mode="numeric",length=length(choice))
  benefits<-vector(mode="numeric",length=length(choice))
  

  #initial state and benefits
  
  
  state[1]=int_state
  
  benefits[1]=p*choice[1]-(a*state[1]-b*state[1]^2)
  
  for(i in 2:length(choice)){
    
# Add the stock dyanmics
    
    state[i]=state[i-1]*(1-gamma)+alpha*choice[i-1] #Add the time from the choice to the state
    
  benefits[i]=p*choice[i]-(a*state[i]-b*state[i]^2)
             
  }
  
  #define period and discount
  t=seq(from=0,length.out=length(benefits))
  
  pv=discount^t*benefits
  
  
  return(data.frame(t=t,PV=pv,Z=state,q=choice))

}

tbl_3a=round(stock(out_3a$solution),1)

kable(tbl_3a)
```


## Stock Midterm Example

obj_fcn_stock<-function(choice,int_state,a,b,gamma,p,alpha,discount,target){
  
  
    #make storage vectors
  state<-vector(mode="numeric",length=0)
  benefits<-vector(mode="numeric",length=length(choice))
  

  #initial state and benefits
  
  
  state[1]=int_state
  
  benefits[1]=p*choice[1]-(a*state[1]-b*state[1]^2)
  
  for(i in 2:length(choice)){
    
# Add the stock dyanmics
    
    state[i]=state[i-1]*(1-gamma)+alpha*choice[i-1] #Add the time from the choice to the state
    
    
  benefits[i]=p*choice[i]-(a*state[i]-b*state[i]^2)
       
             
  }
  
  
  #define period
  t=seq(from=0,length.out=length(benefits))
  
  pv=discount^t*benefits
    
  npv=sum(pv)
  
  return(-npv)
  
  
}

constraint_flow<-function(choice,int_state,a,b,gamma,p,alpha,discount,target){
  
  
  state<-vector(mode="numeric",length=0)
  const<-vector(mode="numeric",length=0)
  #initial state
  state[1]=int_state
  
  for(i in 2:length(choice)){
    
    #State evoles through the choice like in obj function
    state[i]=state[i-1]*(1-gamma)+alpha*choice[i-1] 
    
  }
  
  # Find the state after the last extraction i.e Z11
  
  state_last=state[length(state)]*(1-gamma)+alpha*choice[length(choice)]
  
  
const=state_last-target
  
  return(const)
}



local_opts<-list("algorithm"="NLOPT_LN_COBYLA",xtol_rel=1e-15)
options=list("algorithm"="NLOPT_LN_AUGLAG",xtol_rel=1e-15,maxeval=16000,"local_opts"=local_opts)

# This lets you indicate the value at the end.

period=10

#Use lb to say we cannot have negative extraction

out_3a=nloptr(x0=rep(1,period),eval_f=obj_fcn_stock,
              eval_g_eq=constraint_flow,
              lb=rep(0,period),ub=rep(20,period),opts = options,int_state=40,discount=1/1.04,a=2,b=-.25,gamma=0.2,alpha=2,target=25,p=100)


ta_solution=round(out_3a$solution,5)

ta_value=round(-out_3a$objective,3)

#If we want a table
## Function for making a table

stock<-function(choice,int_state,a=2,b=-0.25,gamma=.2,p=100,alpha=2,discount=1/1.04,target=25){
  
  
    #make storage vectors
  state<-vector(mode="numeric",length=0)
  benefits<-vector(mode="numeric",length=length(choice))
  

  #initial state and benefits
  
  
  state[1]=int_state
  
  benefits[1]=p*choice[1]-(a*state[1]-b*state[1]^2)
  
  for(i in 2:length(choice)){
    
# Add the stock dyanmics
    
    state[i]=state[i-1]*(1-gamma)+alpha*choice[i-1] #Add the time from the choice to the state
    
  benefits[i]=p*choice[i]-(a*state[i]-b*state[i]^2)
             
  }
  
  #define period and discount
  t=seq(from=0,length.out=length(benefits))
 
  
  pv=discount^t*benefits
  
  state_last=state[length(state)]*(1-gamma)+alpha*choice[length(choice)]
  
  return(data.frame(t=t,PV=pv,Z=state,q=choice,state_last=state_last))

}

tbl_3a=round(stock(out_3a$solution,int_state = 40),1)

kable(tbl_3a)
